Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline

### 2017-09-14 draft/ms_v6.tex
Update the draft

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan
% Version 4; Edits from Alexie
% Version 5; Edits from Alexie; Comments by Jim

@@

\def\redm{\texttt{redMaPPer}}
\def\hscpipe{\texttt{hscPipe}}
\def\synpipe{\texttt{SynPipe}}
\def\cmodel{\texttt{cModel}}
\def\forced{\texttt{forced}}
\def\coadd{\texttt{coadd}}
\def\unforced{\texttt{unforced}}
\def\tract{\texttt{tract}}
\def\visit{\texttt{visit}}
\def\tracts{\texttt{tracts}}
\def\visits{\texttt{visits}}
\def\galsim{\texttt{G}{\scriptsize \texttt{AL}}\texttt{S}{\scriptsize \texttt{IM}}}
\def\hst{{\textit{HST}}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}

@@

        \item \song{\synpipe{} works as a special user interface to \hscpipe{}. 
            It will keep developing along with the \hscpipe{} (and \textttt{LSSTpipe}
            in the future). 
            Since both \hscpipe{} and \galsim{} use Python as high-level language, 
            we also choose to use Python for \synpipe{} to make the frequent 
            interactions among them easy and straightforward. 
            Most of the computationally expensive tasks are handled by the low-level 
            algorithms in \hscpipe{} and \galsim{} in C++, the usage of Python will not 
            affect the overall efficiency of \synpipe{}.
            }

@@

    \todo{More discussions}
%% ------------------------------------------------------------------------------------ %%
    %% Other applications
    \song{
    Here we focused on characterizing the photometric performance of \hscpipe{}.  
    However, \synpipe{} is a flexible tool and is being used for a range of other     
    applications. 
    For instance, Murata\etal (in prep.) uses \synpipe{} to characterize the level of
    blending in the HSC Wide Layer.  
    \citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC 
    to search for microlensing events. 
    \synpipe{} is also currently being used to estimate the completeness of high-$z$ 
    LBG and Lyman-$\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.), to 
    check the completeness of high-$z$ LBG pairs as a function of pair separation 
    (Harikane\etal in prep.), to test the completeness of low surface--brightness 
    dwarf galaxies selections (Greco\etal in prep.), and to test magnifications effects
    around nearby clusters (Chiu\etal in prep.).
    }

    %% Future developments
    \song{
    Both \hscpipe{} and \synpipe{} are undergoing active development. 
    Our plan is to update \synpipe{} to provide a photometric benchmark for
    each HSC survey data release, which will help improve \hscpipe{}.
    At the same time, we are also working on improving the efficiency of \synpipe{}.
    Many users are not necessarily concerned with the subtle effects involved in 
    the image stacking process. 
    Hence, a future implementation of \synpipe{} will include the option of injecting 
    objects directly onto \coadd{} images which will speed up the generation of 
    synthetic data sets. 
    The results shown in this paper demonstrate the utility of the \synpipe{} framework
    in order to perform end-to-end quality control on pipeline products to the level 
    of accuracy needed by large panchromatic surveys. 
    }

@@

    %% Short summary
    In February 2017, the HSC survey made its first public data release, and the survey 
    continues to produce increasingly larger amounts of high-quality imaging data.
    To help achieve the designed goals of the survey and to facilitate scientific 
    investigations, we have developed \synpipe{}, a flexible framework based on
    \hscpipe{} and that can be used to perform quality control on the HSC pipeline 
    outputs. 
    \synpipe{} operates by injecting synthetic stars and galaxies into single-\visit{}
    images. 
    These data are then processed by \hscpipe{} to generate \coadd{} images and to 
    perform photometric measurements. 
    With this approach, \synpipe{} can be used as an end-to-end and realistic test of 
    the full data reduction process. 
    In this paper, we use two \tracts{} in the HSC Wide layer with representative 
    seeing conditions (\texttt{goodSeeing} with FWHM$=0.45$\asec{} seeing; 
    \texttt{badSeeing} with FWHM$=0.70$\asec{} seeing) to test the general behaviors 
    of HSC photometry for both stars and galaxies.

>>>>

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan
% Version 4; Edits from Alexie
% Version 5; Edits from Alexie; Comments by Jim
% Version 6; Edits from SH; responses to the referee report

@@

\def\redm{\texttt{redMaPPer}}
\def\hscpipe{\texttt{hscPipe}}
\def\synpipe{\texttt{SynPipe}}
\def\cmodel{\texttt{CModel}}
\def\psf{\texttt{PSF}}
\def\forced{\texttt{forced}}
\def\coadd{\texttt{coadd}}
\def\unforced{\texttt{unforced}}
\def\tract{\texttt{tract}}
\def\visit{\texttt{visit}}
\def\tracts{\texttt{tracts}}
\def\visits{\texttt{visits}}
\def\galsim{\texttt{G}{\scriptsize \texttt{AL}}\texttt{S}{\scriptsize \texttt{IM}}}
\def\hst{{\textit{HST}}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}

@@

        \item \song{\synpipe{} works as a special user interface to \hscpipe{}. 
            It will keep developing along with the \hscpipe{} (and \texttt{LSSTpipe}
            in the future). 
            Since both \hscpipe{} and \galsim{} use Python as high-level language, 
            we also choose to use Python for \synpipe{} to make the frequent 
            interactions among them easy and straightforward. 
            Most of the computationally expensive tasks are handled by the low-level 
            algorithms in \hscpipe{} and \galsim{} in C++, the usage of Python will not 
            affect the overall efficiency of \synpipe{}.
            }

@@

    \song{
    Motivated mainly by observational cosmology and time-domain astrophysics, we are 
    witnessing an exciting time for modern imaging survey.  
    At the same time, more and more sophisticated observational strategy and complex 
    data reduction process adopted by these surveys require more careful tests to 
    fully understand all systematic issues and thoroughly evaluate the qualities of 
    scientific outputs. 
    In this work, we present \synpipe, a Python-based framework to test the performance
    of \hscpipe{} for HSC SSP. 
    }

    \song{
    Similar tools have been developed for DES (\citealt{DES2005}). 
    For instance, \citet{Chang2015} designed a forward-modeling simulation framework 
    to test the ``transfer function'' (from photons to tabulated photometric 
    measurements) of DES data reduction pipeline using simulated images. 
    In a different effort, \citet{Suchyta2016} developed \texttt{BALROG}, a software
    that characterizes measurement biases in DES data reduction through injecting fake
    objects on the coadded DES images.  
    Comparing to these works, the main advantage of \synpipe{} is that it 
    \emph{enables us to conduct tests under more realistic situations.}
    Injecting synthetic objects to real single-exposure image, and follow the entire 
    data reduction process (including image warping and stacking process) make sure that 
    all realistic features on the image and systematics in each step of data reduction 
    can be taken into account.
    }

    \song{
    Here we focused on characterizing the photometric performance of \hscpipe{}.  
    However, \synpipe{} is a flexible tool and is being used for a range of other     
    applications. 
    For instance, Murata\etal (in prep.) uses \synpipe{} to characterize the level of
    blending in the HSC Wide Layer.  
    \citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC 
    to search for microlensing events. 
    \synpipe{} is also currently being used to estimate the completeness of high-$z$ 
    LBG and Lyman-$\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.), to 
    check the completeness of high-$z$ LBG pairs as a function of pair separation 
    (Harikane\etal in prep.), to test the completeness of low surface--brightness 
    dwarf galaxies selections (Greco\etal in prep.), and to test magnifications effects
    around nearby clusters (Chiu\etal in prep.).
    Moreover, \synpipe{} is not being incorporated into the data reduction pipeline
    for LSST, and will also be used to test its performance in the future.
    }

    %% Future developments
    \song{
    Both \hscpipe{} and \synpipe{} are undergoing active development and still face 
    some problems and limitations. 
    At the current stage, \synpipe{} can still not test the impact of background 
    subtraction and PSF model on the performance of photometry.  
    For a more comprehensive summary of the current caveat of HSC data, please 
    see Section~5.8 of \citet{HSCDR1}. 
    In the next section, we will also summarize the issues with \hscpipe{} that are 
    identified by our \synpipe{} tests.
    }

    \song{
    In the near future, we plan to update \synpipe{} to provide a photometric benchmark 
    for each HSC SSP data release and help improve \hscpipe{} along the way.
    At the same time, we are also working on improving the efficiency of \synpipe{}.
    Many users are not necessarily concerned with the subtle effects involved in 
    the image stacking process. 
    Hence, a future implementation of \synpipe{} will include the option of injecting 
    objects directly onto \coadd{} images which will speed up the generation of 
    synthetic data sets. 
    }

@@

    %% Short summary
    In February 2017, the HSC survey made its first public data release, and the survey 
    continues to produce increasingly larger amounts of high-quality imaging data.
    To help achieve the designed goals of the survey and to facilitate scientific 
    investigations, we have developed \synpipe{}, a flexible framework based on
    \hscpipe{} and that can be used to perform quality control on the HSC pipeline 
    outputs. 
    \synpipe{} operates by injecting synthetic stars and galaxies into single-\visit{}
    images. 
    These data are then processed by \hscpipe{} to generate \coadd{} images and to 
    perform photometric measurements. 
    With this approach, \synpipe{} can be used as an end-to-end and realistic test of 
    the full data reduction process. 
    In this paper, we use two \tracts{} in the HSC Wide layer with representative 
    seeing conditions (\texttt{goodSeeing} with FWHM$=0.45$\asec{} seeing; 
    \texttt{badSeeing} with FWHM$=0.70$\asec{} seeing) to test the general behaviors 
    of HSC photometry for both stars and galaxies.
    The results shown in this paper demonstrate the utility of the \synpipe{} framework
    in order to perform end-to-end quality control on pipeline products to the level 
    of accuracy needed by large panchromatic surveys.
